---
title: "IMDB TV ratings from 1990-2018"
output: 
  flexdashboard::flex_dashboard:
    storyboard: true
---

```{r setup, include=FALSE}
library(flexdashboard)
library(tidyverse)
library(lubridate)
library(ggthemes)
library(broom)
library(ggbeeswarm)
library(tidytext)
library(ggpubr)
library(plotly)
library(DT)
library(readr)
library(tidytext)
library(networkD3)
library(forcats)
```

```{r}
#read in the data (long, one row per season)
ratings <- read_csv("../data/IMDb_Economist_tv_ratings.csv")
ratings <- ratings %>% 
  mutate(periode = cut(x = date, 
                     breaks = c(ymd("1980-01-01"), ymd("1990-01-01"),
                                ymd("2000-01-01"), ymd("2010-01-01"),
                                ymd("2019-12-31")),
                     labels=c("1980s","1990s",
                              "2000s","2010s")))

```

```{r}
#wide version of the data (one row per show)
wide_ratings <- ratings %>% pivot_wider(id_cols = c(title, genres, periode),
                        names_from = seasonNumber,
                        names_prefix = "season_",
                        names_sort = TRUE,
                        values_from = av_rating,
                        values_fill = NA) %>% 
                unnest(cols = season_1:season_44)
```

### Graph Visualization of Genre Bigrams Corresponding to TV Shows

```{r carlos}
#load data 

shows <- read_csv("../data/IMDb_Economist_tv_ratings.csv") 

#make nodes 
force_nodes_5.1 <- shows %>%
  select(title, genres) %>%
  tibble() %>%
  group_by(title) %>% 
  unique() %>%
  unnest_tokens(output = describers, input = genres, token = "regex", pattern = ",") %>% 
  ungroup() %>%
  filter(describers != "drama") %>%
  mutate(decade = "All") %>%
  mutate(describers = gsub("-", "", describers)) %>%
  group_by(decade) %>% 
  count(describers, sort = TRUE) %>%
  select(describers, decade, n) %>%
  mutate(describer_deacade = paste(describers, decade, sep = "-")) %>%
  select(describer_deacade, n, decade) %>%
  as.data.frame() %>%
  filter(!agrepl("mystery crime-All", describer_deacade),
         !agrepl("scifi drama-All", describer_deacade), 
         !agrepl("thriller crime-All", describer_deacade))


force_nodes_10 <- shows %>%
  select(!share) %>%
  select(!seasonNumber) %>%
  mutate(date = (ymd(date))) %>%
  mutate(start_year = year(date)) %>%
  group_by(title) %>%
  filter(start_year == min(start_year)) %>%
  select(title, genres, start_year) %>%
  mutate(decade = ifelse(start_year %in% 1990:1999, "90's", ifelse(start_year %in% 2000:2009, "00's","10's"))) %>%
  mutate(genres = gsub("-", "", genres)) %>%
  tibble() %>%
  group_by(title, decade) %>% 
  unique() %>%
  unnest_tokens(output = describers, input = genres, token = "regex", pattern = ",") %>% 
  filter(describers != "drama") %>%
  select(describers, decade) %>%
  group_by(decade) %>% 
  count(describers, sort = TRUE) %>% 
  select(describers, decade, n) %>%
  mutate(describer_deacade = paste(describers, decade, sep = "-")) %>%
  select(describer_deacade, n, decade) %>%
  as.data.frame() %>%
  full_join(force_nodes_5.1) 



#make links 

force_links_3.1 <- shows %>%
  select(title, genres) %>%
  group_by(title) %>% 
  unique() %>%
  tibble() %>%
  mutate(genres = gsub("-", "", genres)) %>%
  mutate(genres = gsub("Drama", "", genres)) %>%
  mutate(genres = gsub("Drama,", "",genres)) %>%
  unnest_tokens(output = describer_bigrams, input = genres, token = "ngrams", n = 2) %>% 
  separate(describer_bigrams, c("word1", "word2"), sep = " ") %>%
  filter(!is.na(word1), 
         !is.na(word2)) %>%
  count(word1, word2, sort = TRUE) %>%
  ungroup() %>%
  mutate(decade = "All", 
         word1 = paste(word1, decade, sep = "-"), 
         word2 = paste(word2, decade, sep = "-")) %>%
  rename(describer_deacade1 = word1, 
         describer_deacade2 = word2) %>%
  select(!decade) %>%
  as.data.frame()

force_links_8 <- shows %>%
  select(!share) %>%
  select(!seasonNumber) %>%
  mutate(date = (ymd(date))) %>%
  mutate(start_year = year(date)) %>%
  group_by(title) %>%
  filter(start_year == min(start_year)) %>%
  select(title, genres, start_year) %>%
  mutate(decade = ifelse(start_year %in% 1990:1999, "90's", ifelse(start_year %in% 2000:2009, "00's","10's"))) %>% 
  tibble() %>%
  mutate(genres = gsub("-", "", genres)) %>%
  mutate(genres = gsub("Drama", "", genres)) %>%
  mutate(genres = gsub("Drama,", "",genres)) %>%
  unnest_tokens(output = describer_bigrams, input = genres, token = "ngrams", n = 2) %>% 
  separate(describer_bigrams, c("word1", "word2"), sep = " ") %>%
  filter(!is.na(word1), 
         !is.na(word2)) %>%
  mutate(describer_deacade1 = paste(word1, decade, sep = "-"),
         describer_deacade2 = paste(word2, decade, sep = "-")) %>%
  count(describer_deacade1, describer_deacade2, sort = TRUE) %>%
  ungroup() %>%
  as.data.frame() %>%
  full_join(force_links_3.1) %>%
  mutate(describer_deacade1 = factor(describer_deacade1, levels = force_nodes_10$describer_deacade)) %>%
  mutate(describer_deacade1 = as.numeric(describer_deacade1) - 1) %>%
  mutate(describer_deacade2 = factor(describer_deacade2, levels = force_nodes_10$describer_deacade)) %>%
  mutate(describer_deacade2 = as.numeric(describer_deacade2) - 1)

#make big force net 

forcenet_5 <- forceNetwork(Links = force_links_8, Nodes = force_nodes_10, 
                           Source = "describer_deacade1", Target = "describer_deacade2", 
                           Value = "n", NodeID = "describer_deacade",  zoom = TRUE, 
                           Nodesize = "n", Group = "decade", opacityNoHover = 1, 
                           opacity = .6, legend = TRUE, fontSize = 10, charge = -50, 
                           colourScale = JS("d3.scaleOrdinal(d3.schemeCategory10);"))

forcenet_5
```

***

Nodes denote genres, size of nodes denote total number of times geanre appeared, edge thickness indicates number of co-occurrence. The four networks are divided by decade in which the first season of the show aired, except for “All” for which all interactions are shown.

### Average Rating Per Genres


```{r maelle}
rating_genre <- ratings %>% 
  group_by(title) %>% 
  nest() %>% 
  mutate(overall_rating= 
           map(data, 
               ~ (sum(.x$av_rating)/nrow(.x)))) %>% 
   ungroup() %>%
  unnest(cols = c(data, overall_rating)) %>% 
  separate(genres,into=c("genre1","genre2","genre3")
           ,sep = ",") %>% 
  pivot_longer(cols = c("genre1","genre2","genre3"),
               values_to = "genre") %>% 
  filter(!is.na(genre), seasonNumber==1) %>% 
  mutate(periode = cut(x = date, 
                     breaks = c( ymd("1980-01-01"),ymd("1990-01-01"),
                                ymd("2000-01-01"),ymd("2010-01-01"),
                                ymd("2019-12-31")),
                     labels=c("80's","90's",
                              "2000-2009","2010-2018")))  
  
 rating_genre <-rating_genre %>%  
  mutate(genre=fct_lump_n(genre, 7)) %>% 
  filter(genre!="Other")

  
nitys <- rating_genre %>% 
  filter(periode == "90's") %>% 
    plot_ly(x = ~overall_rating,
            y = ~genre,
            split = ~genre,
            orientation ="h",
    type = 'violin',
    box = list(visible = T),
    meanline = list(visible = T),  
    color = ~genre,
    showlegend=FALSE,
    text= ~paste('</br> Title: ', title, 
                 '</br> Rating:', overall_rating),
    points="suspectedoutliers",
    hoverinfo='text',
    scalemode="count"
    ) 
nitys <- nitys %>%
layout(
  yaxis=list(
    title=' Genre'),
  xaxis=list(title='
             </br> Rating' ))


  
two <- rating_genre %>% 
  filter(periode == "2000-2009") %>% 
    plot_ly(x = ~overall_rating,
            y = ~genre,
            split = ~genre,
            orientation ="h",
    type = 'violin',
    box = list(visible = T),
    meanline = list(visible = T),  
    color = ~genre,
    showlegend=FALSE,
    text= ~paste('</br>Title: ', title, '</br> Rating:', overall_rating),
    scalemode="count",
    points="suspectedoutliers",
    hoverinfo='text') 
two <- two %>%
layout(
  yaxis=list(
    title=' Genres'),
  xaxis=list(title='
             </br> Rating',
             range=c(4, 10)))

 twoten <- rating_genre %>% 
  filter(periode == "2010-2018") %>% 
    plot_ly(x = ~overall_rating,
            y = ~genre,
            split = ~genre,
            orientation ="h",
    type = 'violin',
    box = list(visible = T),
    meanline = list(visible = T),
    scalemode="count",
    color = ~genre,
    showlegend=FALSE,
    text= ~paste('</br> Title: ', title, 
                 '</br> Rating:', overall_rating),
    points="suspectedoutliers",
    hoverinfo='text')  
    
twoten <- twoten %>%
layout(
 yaxis=list(
    title= 'Genres'),
  xaxis=list(title='
             </br> Rating' ))

annotations <- list( list( 
  x = 0.2,  
  y = 1.0,  
  text = '<b> 1990-1999 </b>',
  xref = "paper",  
  yref = "paper",  
  xanchor = "center",  
  yanchor = "bottom", showarrow = FALSE ),  

  list( x = 0.5,  
        y = 1,  
        text = '<b> 2000-2009 </b>',
        xref = "paper",  
        yref = "paper",  
        xanchor = "center",  
        yanchor = "bottom",  
        showarrow = FALSE ),  
  list( x = 0.9,  
        y = 1.0,  
        text = '<b> 2010-2018 </b>',
        xref = "paper",  
        yref = "paper",  
        xanchor = "center", 
        yanchor = "bottom",  
        showarrow = FALSE ))

subplot(nitys,two,twoten, shareY = TRUE, 
        titleY =TRUE, titleX = TRUE, shareX = FALSE ) %>% 
  layout(annotations = annotations)

  


  
  
  

```

***
Violin plot of the average rating per genres for 3 different decades. The outliers dot are interactive and show the rating and the title of the specific TV show. 



### Top 10 Rated Shows per Year


```{r megan}
#Interactive table of top shows by year
top_shows <- ratings %>%
  select(title, date, av_rating, genres) %>%
  mutate(date = ymd(date),
         year = year(date)) 

top_10 <- top_shows %>%
  group_by(year) %>%
  select(year, title, av_rating, genres) %>%
  slice_max(av_rating,n = 10) 

datatable(top_10, colnames = c("Year", "Show Name", "Rating", "Genres")) %>%
  formatStyle("av_rating", 
              background = styleColorBar(top_10$av_rating, 'lightblue'),
              backgroundSize = '98% 88%',
              backgroundRepeat = 'no-repeat',
              backgroundPosition = 'center')
  

```

***
Add information about the data (including the data source) as well as what the dashboard can be used to explore and how to navigate it.

The data table includes every show that had the highest 10 ratings by year between 1990 and 2018. One can search a year to see the top 10 shows of that year or search a show to see what year that show appeared in the top 10 as well. 

### Do shows that got renewed for a second season have better first season ratings?

```{r casey}
renew <- ratings %>%
  group_by(title) %>%
  mutate(overall_rat = mean(av_rating),
         renewed = max(seasonNumber > 1)) %>% 
  filter(seasonNumber == 1) %>% 
  summarize(title = title,
            renewed = as.logical(renewed),
            season1rating = av_rating,
            periode = periode)

nested_renew <- renew %>% group_by(periode) %>% nest()

renewed_stats <- nested_renew %>% 
  mutate(t_test = purrr::map(data, ~t.test(.x$season1rating ~ .x$renewed), data=.x)) %>% 
  mutate(summary = purrr::map(t_test, broom::glance)) %>% 
  unnest(cols=c(data,summary)) %>%
  ungroup() %>% 
  dplyr::select(periode, title, p.value) %>% 
  group_by(periode) %>% 
  mutate(shows = length(title)) %>%
  ungroup() %>%
  select(-title) %>% 
  unique() %>% 
  mutate(p.value = signif(p.value, digits=3),
         group1=FALSE,
         group2=TRUE) %>% 
  mutate(p.value = if_else(p.value < 5e-2, true=as.character(p.value), false="n.s."))

renew_text <- data.frame(
  label = c("n.s.", "p=0.0132", "p=6.64e-12"),
  periode   = c("1990s", "2000s", "2010s"),
  x = c(FALSE, FALSE, FALSE),
  y = c(10.25, 10.25, 10.25)
)

renew_plot <- renew %>% 
  ggplot(aes(x=renewed, y=season1rating)) +
  stat_summary(fun = 'mean', geom="bar", fill="grey70") +
  geom_point(alpha=0.25) +
  facet_wrap(~periode) + 
  labs(x="Show Renewed",
       y = "Season 1 Rating") +
  theme(legend.position = "none") +
  geom_text(data = renew_text,
            mapping = aes(x=x, y=y, label=label),
            nudge_x=0.5) +
  scale_y_continuous(expand = expansion(mult = c(0, 0.1)))

ggplotly(renew_plot)
# will try to have the info in this table
# (# shows Renewed or Not by decade)
# pop up when you scroll over each bar

#renew %>% group_by(periode, renewed) %>% summarise(n=n())
```


***
Each dot shows the season 1 rating for a particular show. Shows are grouped by whether they only had one season (renewed=FALSE) or were renewed for at least a second season (renewed=TRUE). The low p-values for the 2000s and 2010s indicate that shows that were renewed did have better rated first seasons than unrenewed shows, but in the 1990s this was not the case. The statistical power may be worse for the 1990s since there were fewer shows (n=69) than in the 2000s (n=195) or 2010s (n=590).